cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_unifcube

>>>>

The `gen_unifcube(n, p)` function generates $n$ points uniformly distributed within a $3\text{-}D$ cube centered at the origin, optionally embedded in a higher-dimensional space with additional noise dimensions.

Points are sampled independently from $X\_1, X\_2, X\_3 \sim \mathcal{U}(-0.5, 0.5)$ of a cube of side length 1. This results in a uniform cloud of points filling the unit cube in $3\text{-}D$ space.

For $p > 3$, the remaining dimensions are filled with Gaussian noise:

$$
X\_j \sim \mathcal{N}(0, 0.05^2), \quad j = 4, \dots, p.
$$
